### 2023-12-03 chapters/conclusion.tex
Fix decision-support -> decision support

\textbf{\Cref{chp:introduction}} introduced the motivational cases of automated medical coding and stroke recognition and used them to exemplify the importance of out-of-distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision-support and considered potential sources of uncertainty and ideal model behavior. 
The cases form a reference point for the thesis as a whole, connecting its contributions within out-of-distribution detection and representation learning back to practical applications. 
In this conclusion, we will review the studies presented in previous chapters in the context of the discussion of \cref{chp:discussion}, the recent progress in the field, and point to interesting directions of future research.
As \textbf{\cref{chp:main-contributions}} already details the contributions made by this thesis, we will not reiterate them in detail in this conclusion.

@@

The formulation of OOD detection as a statistical test also allows for better guarantees for such systems in practice. For instance, as also discussed in \cref{chp:paper-modelagnostic}, the statistical framework enables false positive rate control which is a valuable property in many practical applications especially if they involve high-risk actions such as in medical decision-support.

>>>>

\textbf{\Cref{chp:introduction}} introduced the motivational cases of automated medical coding and stroke recognition and used them to exemplify the importance of out-of-distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision support and considered potential sources of uncertainty and ideal model behavior. 
The cases form a reference point for the thesis as a whole, connecting its contributions within out-of-distribution detection and representation learning back to practical applications. 
In this conclusion, we will review the studies presented in previous chapters in the context of the discussion of \cref{chp:discussion}, the recent progress in the field, and point to interesting directions of future research.
As \textbf{\cref{chp:main-contributions}} already details the contributions made by this thesis, we will not reiterate them in detail in this conclusion.

@@

The formulation of OOD detection as a statistical test also allows for better guarantees for such systems in practice. For instance, as also discussed in \cref{chp:paper-modelagnostic}, the statistical framework enables false positive rate control which is a valuable property in many practical applications especially if they involve high-risk actions such as in medical decision support.
